Short-term hourly forecasting for care services

### 2021-09-24 paper/paper.Rmd
Text on GAMLSS and evaluation

In order to assess performance of models, we track quantiles (5th, 10th, etc up to 95th quantile) and conditional expectations for 48 steps ahead for each model. The forecasts are produced every 12 hours for the holdout of 365 days in a rolling origin fashion [@Tashman2000], resulting in 727 origins. Based on these values, several error measures are calculated to evaluate the performance of models in terms of specific quantiles and in terms of expectation. The latter is measured via Root Mean Squared Error (RMSE):
\begin{equation}
  \mathrm{RMSE} = \sqrt{\frac{1}{n} \sum_{j=1}^n e_j^2} .
  (\#eq:RMSE)
\end{equation}
When it comes to quantile performance, we used pinball, and all the other cool things described by Jethro.

Also see Equation \@ref(eq:RMSE)

>>>>

In order to assess performance of models, we track quantiles (5th, 10th, etc up to 95th quantile) and conditional expectations for 48 steps ahead for each model. The forecasts are produced every 12 hours for the holdout of 365 days in a rolling origin fashion [@Tashman2000], resulting in 727 origins. Based on these values, several error measures are calculated to evaluate the performance of models in terms of specific quantiles and in terms of expectation. The latter is measured via Root Mean Squared Error (RMSE):
\begin{equation}
  \mathrm{RMSE} = \sqrt{\frac{1}{n} \sum_{j=1}^n e_j^2} .
  (\#eq:RMSE)
\end{equation}

The objective of density forecasts it to be as sharp as possible while remaining reliable/calibrated [@Gneiting2007a]. A forecast is said to be sharp if the predictive distribution has a relatively small spread, indicating low uncertainty, witch is valuable to decision makers provided the forecast is calibrated.

The Pinball Score is a strictly proper score used to evaluate quantile forecasts and is the discrete form of the Continuous Rank Probability Score. It rewards sharpness and penalises mis-calibration, so measures all-round performance, however, calibration should still be verified separately. Furthermore, 
The Pinball Score for an individual quantile matches the loss function minimised in quantile regression model estimation. The Pinball Score is given by
\begin{equation}
    % \text{Pinball} = 
    \frac{1}{T|\mathcal{A}|} \sum_{\alpha \in \mathcal{A}} \sum_{t=1}^T
 \left(q_{\alpha,t} - y_{t} \right)
 \left(\mathbb{1}(y_{t}\leq_{\alpha,t})-\alpha \right)
 (\#eq:pinball)
\end{equation}
where $\mathcal{A} = {0.05,0.1,...,0.95}$ is the set of quantiles being estimated.

Calibration, also called `reliability', is the property that forecast probabilities match the observed frequency of realisations. If a forecast is calibrated, then 20\% of observations should fall below the $\alpha=0.2$ predictive quantile (with some tolerance based on the finite sample size). This property is necessary for forecast probabilities to be used in quantitative decision-making. Calibration is typically evaluated visually using reliability diagrams, which plot the nominal coverage, $\alpha$, against observer frequency mean($\mathbb{1}(y_{t}\le q_{\alpha,t})$).
